Code used to generate paper results : Database comparison and CT characteristics

### 2024-05-30 Paper_code-Database_Comparison.Rmd
Added small analyses for database comparison

@@

table(new$testis_specificity)
table(new$X_linked)
table(new$regulated_by_methylation)
table(new$X_linked, new$regulated_by_methylation)
TCGA_expression(tumor = "all", genes = new$external_gene_name, 
                units = "log_TPM")
TCGA_expression(tumor = "all", 
                genes = filter(new, X_linked & regulated_by_methylation)$external_gene_name, 
                units = "log_TPM")
```

>>>>

```{r}
all_genes %>%
  filter(external_gene_name %in% CTdatabase_ours@IntersectionSets[["10"]]) %>% 
  pull(regulated_by_methylation) %>% 
  table()

all_genes %>%
  filter(external_gene_name %in% CTdatabase_ours@IntersectionSets[["10"]]) %>% 
  pull(transcript_biotype) %>% 
  table()
table(CT_genes$transcript_biotype)
#45 lncRNA in all CT_genes

all_genes %>%
  filter(external_gene_name %in% CTdatabase_ours@IntersectionSets[["10"]]) %>% 
  pull(CpG_promoter) %>% 
  table()
table(CT_genes$CpG_promoter)

all_genes %>%
  filter(external_gene_name %in% CTdatabase_ours@IntersectionSets[["10"]])

@@

table(new$testis_specificity)
table(new$X_linked)
table(new$regulated_by_methylation)
table(new$X_linked, new$regulated_by_methylation)
table(new$CpG_promoter)
TCGA_expression(tumor = "all", genes = new$external_gene_name, 
                units = "log_TPM")
TCGA_expression(tumor = "all", 
                genes = filter(new, X_linked & regulated_by_methylation)$external_gene_name, 
                units = "log_TPM")
testis_expression(genes = new$external_gene_name, "germ_cells")
```
